Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-22 paper/v2/paper-edited.tex
edits

We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies for Microsoft's datacenter and backbone networks.
% and compared these specifications with existing configurations.
We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds or thousands of routers, compiling in under 9 minutes in all cases.

@@

We obtained routing policy for Microsoft's backbone network and datacenters. Multiple datacenters share this policy. The backbone network connects to the datacenters and also has many external BGP neighbors. The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has a less regular structure).

>>>>

We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies for datacenter and backbone networks.
% and compared these specifications with existing configurations.
We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds or thousands of routers, compiling in under 9 minutes in all cases.

@@

We obtained routing policy for the backbone network and datacenters of a large cloud provider. Multiple datacenters share this policy. The backbone network connects to the datacenters and also has many external BGP neighbors. The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has a less regular structure).
